---
title: "Tutorial for inferring dynamic lncRNA causal regulation in autism spectrum disorder" 
author: "\\
    
    Junpeng Zhang (zjp@dali.edu.cn)\\
    
    School of Engineering, Dali University"
date: '`r Sys.Date()`'
output:
    BiocStyle::html_document:
      toc: yes
    BiocStyle::pdf_document:
      toc: yes
vignette: >
    %\VignetteIndexEntry{Tutorial for inferring dynamic lncRNA causal regulation in autism spectrum disorder} 
    %\VignetteEngine{knitr::rmarkdown} 
    %\usepackage[utf8]{inputenc} 
    %\VignetteEncoding{UTF-8}
---

```{r style, echo=FALSE, results="asis", message=FALSE}
BiocStyle::markdown()
knitr::opts_chunk$set(tidy = FALSE,
    warning = FALSE,
    message = FALSE)
```

# Introduction
Conventional static causal inference methods fail to capture the dynamic interplay of lncRNAs across diverse brain biological contexts. Here, we develop a hidden causality-based method Clean to infer dynamic lncRNA causal regulation in autism spectrum disorder (ASD). In this tutorial, we will show how to apply Clean into new data.

# Load required R packages
Clean employs a hidden causality inference to delineate dynamic causal regulation by lncRNAs across diverse ASD biological contexts, such as diagnosis, region, age, sex, and cell type. Before applying Clean into new data, users need to install and load the the following 17 R packages. 

```{r, eval=TRUE, include=TRUE}
# Load required R packages
library(doParallel)
library(lmtest)
library(pracma)
library(robustbase)
library(vars)
library(dynlm)
library(SuperCell)
library(MetacellAnalysisToolkit)
library(Seurat)
library(patterncausality)
library(dplyr)
library(igraph)
library(energy)
library(SCORPIUS)
library(e1071)    
library(caret)    
library(pROC)
```

# Data preparation
For inferring dynamic causal regulation by lncRNAs, users should prepare matched lncRNA and mRNA expression data and putative lncRNA-target interactions. In this tutorial, we use the largest single-nucleus RNA sequencing (snRNA-seq) data of cortical tissue including the anterior cingulated (ACC) and prefrontal cortex (PFC) regions from patients with autism (the expression data of 813 lncRNAs and 5,133 mRNAs exhibiting high expression levels across 104,559 cells, including 52,003 autism cells and 52,556 control cells) as an example. Putative lncRNA-target interactions are predicted by using LncTar (http://www.cuilab.cn/lnctar). In total, a list of 105,649 lncRNA-mRNA interactions has been predicted by LncTar.

```{r, eval=TRUE, include=TRUE}
# Load ASD dataset
load("data/ASD_lncR_mR.RData")

# Index of cause and effect for causal inference
cause <- 5134:5946
effect <- 1:5133

# Priori information of lncRNA targets
lncRTarget_priori <- as.matrix(read.csv("LncTar.csv", header = TRUE, sep=","))
lncRTarget_priori_graph <- make_graph(c(t(lncRTarget_priori[, 1:2])), directed = FALSE)

# Groundtruth of lncRNA targets
lncRTarget_groundtruth <- as.matrix(read.csv("RegNetwork_high+medium.csv", header = TRUE, sep=","))
lncRTarget_groundtruth_graph <- make_graph(c(t(lncRTarget_groundtruth[, 1:2])), directed = FALSE)
```

For convenience, the full list of our prepared single-nucleus RNA sequencing data, priori information of lncRNA targets, groundtruth of lncRNA targets, and putative ligand-receptor interactions in the Clean paper can be obtained from [here](https://drive.google.com/file/d/1sdLk7AcZszXYdV47_EMEVVhf0p1E_vDo/view?usp=drive_link).

# Delineating dynamic lncRNA regulation in ASD 
The utility functions for delineating dynamic lncRNA causal regulation are collected in the source file: **Clean.R**. In this tutorial, we select three sequential causality methods (Clean, Granger, seqICP) to infer dynamic lncRNA causal regulation from ASD single-nucleus RNA sequencing data. The priori information of lncRNA targets has two cases: None (no priori information), LncTar (priori information of LncTar).

## Step 1: Identifying metacells
```{r, eval=TRUE, include=TRUE}
# ASD
ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_mRNAs_data, ASD_lncRNAs_data)),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_mRNAs_data, ASD_lncRNAs_data)), ASD_SC30$membership)
colnames(ASD_SC30_GE) <- paste("MC", seq(ncol(ASD_SC30_GE)), sep = "")

# Control
Control_SC30 <- SCimplify(as.matrix(rbind(Control_mRNAs_data, Control_lncRNAs_data)),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_mRNAs_data, Control_lncRNAs_data)), Control_SC30$membership)
colnames(Control_SC30_GE) <- paste("MC", seq(ncol(Control_SC30_GE)), sep = "")

# ACC_ASD
ACC_ASD_SC30 <- SCimplify(as.matrix(rbind(ACC_ASD_mRNAs_data, ACC_ASD_lncRNAs_data)),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
ACC_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ACC_ASD_mRNAs_data, ACC_ASD_lncRNAs_data)), ACC_ASD_SC30$membership)
colnames(ACC_ASD_SC30_GE) <- paste("MC", seq(ncol(ACC_ASD_SC30_GE)), sep = "")

# ACC_Control
ACC_Control_SC30 <- SCimplify(as.matrix(rbind(ACC_control_mRNAs_data, ACC_control_lncRNAs_data)),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
ACC_Control_SC30_GE <- supercell_GE(as.matrix(rbind(ACC_control_mRNAs_data, ACC_control_lncRNAs_data)), ACC_Control_SC30$membership)
colnames(ACC_Control_SC30_GE) <- paste("MC", seq(ncol(ACC_Control_SC30_GE)), sep = "")

# PFC_ASD
PFC_ASD_SC30 <- SCimplify(as.matrix(rbind(PFC_ASD_mRNAs_data, PFC_ASD_lncRNAs_data)),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
PFC_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(PFC_ASD_mRNAs_data, PFC_ASD_lncRNAs_data)), PFC_ASD_SC30$membership)
colnames(PFC_ASD_SC30_GE) <- paste("MC", seq(ncol(PFC_ASD_SC30_GE)), sep = "")

# PFC_Control
PFC_Control_SC30 <- SCimplify(as.matrix(rbind(PFC_control_mRNAs_data, PFC_control_lncRNAs_data)),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
PFC_Control_SC30_GE <- supercell_GE(as.matrix(rbind(PFC_control_mRNAs_data, PFC_control_lncRNAs_data)), PFC_Control_SC30$membership)
colnames(PFC_Control_SC30_GE) <- paste("MC", seq(ncol(PFC_Control_SC30_GE)), sep = "")

# Lower18_ASD
Lower18_ASD_SC30 <- SCimplify(as.matrix(rbind(Lower18_ASD_mRNAs_data, Lower18_ASD_lncRNAs_data)),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Lower18_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(Lower18_ASD_mRNAs_data, Lower18_ASD_lncRNAs_data)), Lower18_ASD_SC30$membership)
colnames(Lower18_ASD_SC30_GE) <- paste("MC", seq(ncol(Lower18_ASD_SC30_GE)), sep = "")

# Lower18_Control
Lower18_Control_SC30 <- SCimplify(as.matrix(rbind(Lower18_control_mRNAs_data, Lower18_control_lncRNAs_data)),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Lower18_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Lower18_control_mRNAs_data, Lower18_control_lncRNAs_data)), Lower18_Control_SC30$membership)
colnames(Lower18_Control_SC30_GE) <- paste("MC", seq(ncol(Lower18_Control_SC30_GE)), sep = "")

# Larger18_ASD
Larger18_ASD_SC30 <- SCimplify(as.matrix(rbind(Larger18_ASD_mRNAs_data, Larger18_ASD_lncRNAs_data)),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Larger18_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(Larger18_ASD_mRNAs_data, Larger18_ASD_lncRNAs_data)), Larger18_ASD_SC30$membership)
colnames(Larger18_ASD_SC30_GE) <- paste("MC", seq(ncol(Larger18_ASD_SC30_GE)), sep = "")

# Larger18_Control
Larger18_Control_SC30 <- SCimplify(as.matrix(rbind(Larger18_control_mRNAs_data, Larger18_control_lncRNAs_data)),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Larger18_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Larger18_control_mRNAs_data, Larger18_control_lncRNAs_data)), Larger18_Control_SC30$membership)
colnames(Larger18_Control_SC30_GE) <- paste("MC", seq(ncol(Larger18_Control_SC30_GE)), sep = "")

# Male_ASD
Male_ASD_SC30 <- SCimplify(as.matrix(rbind(Male_ASD_mRNAs_data, Male_ASD_lncRNAs_data)),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Male_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(Male_ASD_mRNAs_data, Male_ASD_lncRNAs_data)), Male_ASD_SC30$membership)
colnames(Male_ASD_SC30_GE) <- paste("MC", seq(ncol(Male_ASD_SC30_GE)), sep = "")

# Male_Control
Male_Control_SC30 <- SCimplify(as.matrix(rbind(Male_control_mRNAs_data, Male_control_lncRNAs_data)),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Male_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Male_control_mRNAs_data, Male_control_lncRNAs_data)), Male_Control_SC30$membership)
colnames(Male_Control_SC30_GE) <- paste("MC", seq(ncol(Male_Control_SC30_GE)), sep = "")

# Female_ASD
Female_ASD_SC30 <- SCimplify(as.matrix(rbind(Female_ASD_mRNAs_data, Female_ASD_lncRNAs_data)),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Female_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(Female_ASD_mRNAs_data, Female_ASD_lncRNAs_data)), Female_ASD_SC30$membership)
colnames(Female_ASD_SC30_GE) <- paste("MC", seq(ncol(Female_ASD_SC30_GE)), sep = "")

# Female_Control
Female_Control_SC30 <- SCimplify(as.matrix(rbind(Female_control_mRNAs_data, Female_control_lncRNAs_data)),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Female_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Female_control_mRNAs_data, Female_control_lncRNAs_data)), Female_Control_SC30$membership)
colnames(Female_Control_SC30_GE) <- paste("MC", seq(ncol(Female_Control_SC30_GE)), sep = "")

# NeuNRGNII_ASD
NeuNRGNII_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["NeuNRGNII_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["NeuNRGNII_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
NeuNRGNII_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["NeuNRGNII_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["NeuNRGNII_ASD_lncRNAs_data"]])), NeuNRGNII_ASD_SC30$membership)
colnames(NeuNRGNII_ASD_SC30_GE) <- paste("MC", seq(ncol(NeuNRGNII_ASD_SC30_GE)), sep = "")

# NeuNRGNII_Control
NeuNRGNII_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["NeuNRGNII_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["NeuNRGNII_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
NeuNRGNII_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["NeuNRGNII_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["NeuNRGNII_control_lncRNAs_data"]])), NeuNRGNII_Control_SC30$membership)
colnames(NeuNRGNII_Control_SC30_GE) <- paste("MC", seq(ncol(NeuNRGNII_Control_SC30_GE)), sep = "")

# L56_ASD
L56_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["L56_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["L56_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
L56_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["L56_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["L56_ASD_lncRNAs_data"]])), L56_ASD_SC30$membership)
colnames(L56_ASD_SC30_GE) <- paste("MC", seq(ncol(L56_ASD_SC30_GE)), sep = "")

# L56_Control
L56_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["L56_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["L56_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
L56_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["L56_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["L56_control_lncRNAs_data"]])), L56_Control_SC30$membership)
colnames(L56_Control_SC30_GE) <- paste("MC", seq(ncol(L56_Control_SC30_GE)), sep = "")

# Oligodendrocytes_ASD
Oligodendrocytes_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["Oligodendrocytes_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["Oligodendrocytes_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Oligodendrocytes_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["Oligodendrocytes_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["Oligodendrocytes_ASD_lncRNAs_data"]])), Oligodendrocytes_ASD_SC30$membership)
colnames(Oligodendrocytes_ASD_SC30_GE) <- paste("MC", seq(ncol(Oligodendrocytes_ASD_SC30_GE)), sep = "")

# Oligodendrocytes_Control
Oligodendrocytes_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["Oligodendrocytes_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["Oligodendrocytes_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Oligodendrocytes_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["Oligodendrocytes_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["Oligodendrocytes_control_lncRNAs_data"]])), Oligodendrocytes_Control_SC30$membership)
colnames(Oligodendrocytes_Control_SC30_GE) <- paste("MC", seq(ncol(Oligodendrocytes_Control_SC30_GE)), sep = "")

# OPC_ASD
OPC_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["OPC_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["OPC_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
OPC_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["OPC_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["OPC_ASD_lncRNAs_data"]])), OPC_ASD_SC30$membership)
colnames(OPC_ASD_SC30_GE) <- paste("MC", seq(ncol(OPC_ASD_SC30_GE)), sep = "")

# OPC_Control
OPC_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["OPC_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["OPC_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
OPC_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["OPC_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["OPC_control_lncRNAs_data"]])), OPC_Control_SC30$membership)
colnames(OPC_Control_SC30_GE) <- paste("MC", seq(ncol(OPC_Control_SC30_GE)), sep = "")

# ASTFB_ASD
ASTFB_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["ASTFB_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["ASTFB_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
ASTFB_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["ASTFB_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["ASTFB_ASD_lncRNAs_data"]])), ASTFB_ASD_SC30$membership)
colnames(ASTFB_ASD_SC30_GE) <- paste("MC", seq(ncol(ASTFB_ASD_SC30_GE)), sep = "")

# ASTFB_Control
ASTFB_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["ASTFB_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["ASTFB_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
ASTFB_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["ASTFB_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["ASTFB_control_lncRNAs_data"]])), ASTFB_Control_SC30$membership)
colnames(ASTFB_Control_SC30_GE) <- paste("MC", seq(ncol(ASTFB_Control_SC30_GE)), sep = "")

# Endothelial_ASD
Endothelial_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["Endothelial_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["Endothelial_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Endothelial_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["Endothelial_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["Endothelial_ASD_lncRNAs_data"]])), Endothelial_ASD_SC30$membership)
colnames(Endothelial_ASD_SC30_GE) <- paste("MC", seq(ncol(Endothelial_ASD_SC30_GE)), sep = "")

# Endothelial_Control
Endothelial_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["Endothelial_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["Endothelial_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Endothelial_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["Endothelial_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["Endothelial_control_lncRNAs_data"]])), Endothelial_Control_SC30$membership)
colnames(Endothelial_Control_SC30_GE) <- paste("MC", seq(ncol(Endothelial_Control_SC30_GE)), sep = "")

# Microglia_ASD
Microglia_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["Microglia_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["Microglia_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Microglia_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["Microglia_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["Microglia_ASD_lncRNAs_data"]])), Microglia_ASD_SC30$membership)
colnames(Microglia_ASD_SC30_GE) <- paste("MC", seq(ncol(Microglia_ASD_SC30_GE)), sep = "")

# Microglia_Control
Microglia_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["Microglia_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["Microglia_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Microglia_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["Microglia_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["Microglia_control_lncRNAs_data"]])), Microglia_Control_SC30$membership)
colnames(Microglia_Control_SC30_GE) <- paste("MC", seq(ncol(Microglia_Control_SC30_GE)), sep = "")

# NeuNRGNI_ASD
NeuNRGNI_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["NeuNRGNI_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["NeuNRGNI_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
NeuNRGNI_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["NeuNRGNI_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["NeuNRGNI_ASD_lncRNAs_data"]])), NeuNRGNI_ASD_SC30$membership)
colnames(NeuNRGNI_ASD_SC30_GE) <- paste("MC", seq(ncol(NeuNRGNI_ASD_SC30_GE)), sep = "")

# NeuNRGNI_Control
NeuNRGNI_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["NeuNRGNI_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["NeuNRGNI_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
NeuNRGNI_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["NeuNRGNI_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["NeuNRGNI_control_lncRNAs_data"]])), NeuNRGNI_Control_SC30$membership)
colnames(NeuNRGNI_Control_SC30_GE) <- paste("MC", seq(ncol(NeuNRGNI_Control_SC30_GE)), sep = "")

# INVIP_ASD
INVIP_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["INVIP_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["INVIP_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
INVIP_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["INVIP_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["INVIP_ASD_lncRNAs_data"]])), INVIP_ASD_SC30$membership)
colnames(INVIP_ASD_SC30_GE) <- paste("MC", seq(ncol(INVIP_ASD_SC30_GE)), sep = "")

# INVIP_Control
INVIP_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["INVIP_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["INVIP_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
INVIP_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["INVIP_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["INVIP_control_lncRNAs_data"]])), INVIP_Control_SC30$membership)
colnames(INVIP_Control_SC30_GE) <- paste("MC", seq(ncol(INVIP_Control_SC30_GE)), sep = "")

# L56CC_ASD
L56CC_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["L56CC_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["L56CC_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
L56CC_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["L56CC_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["L56CC_ASD_lncRNAs_data"]])), L56CC_ASD_SC30$membership)
colnames(L56CC_ASD_SC30_GE) <- paste("MC", seq(ncol(L56CC_ASD_SC30_GE)), sep = "")

# L56CC_Control
L56CC_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["L56CC_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["L56CC_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
L56CC_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["L56CC_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["L56CC_control_lncRNAs_data"]])), L56CC_Control_SC30$membership)
colnames(L56CC_Control_SC30_GE) <- paste("MC", seq(ncol(L56CC_Control_SC30_GE)), sep = "")

# INSV2C_ASD
INSV2C_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["INSV2C_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["INSV2C_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
INSV2C_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["INSV2C_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["INSV2C_ASD_lncRNAs_data"]])), INSV2C_ASD_SC30$membership)
colnames(INSV2C_ASD_SC30_GE) <- paste("MC", seq(ncol(INSV2C_ASD_SC30_GE)), sep = "")

# INSV2C_Control
INSV2C_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["INSV2C_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["INSV2C_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
INSV2C_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["INSV2C_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["INSV2C_control_lncRNAs_data"]])), INSV2C_Control_SC30$membership)
colnames(INSV2C_Control_SC30_GE) <- paste("MC", seq(ncol(INSV2C_Control_SC30_GE)), sep = "")

# L23_ASD
L23_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["L23_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["L23_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
L23_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["L23_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["L23_ASD_lncRNAs_data"]])), L23_ASD_SC30$membership)
colnames(L23_ASD_SC30_GE) <- paste("MC", seq(ncol(L23_ASD_SC30_GE)), sep = "")

# L23_Control
L23_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["L23_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["L23_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
L23_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["L23_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["L23_control_lncRNAs_data"]])), L23_Control_SC30$membership)
colnames(L23_Control_SC30_GE) <- paste("MC", seq(ncol(L23_Control_SC30_GE)), sep = "")

# INPV_ASD
INPV_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["INPV_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["INPV_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
INPV_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["INPV_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["INPV_ASD_lncRNAs_data"]])), INPV_ASD_SC30$membership)
colnames(INPV_ASD_SC30_GE) <- paste("MC", seq(ncol(INPV_ASD_SC30_GE)), sep = "")

# INPV_Control
INPV_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["INPV_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["INPV_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
INPV_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["INPV_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["INPV_control_lncRNAs_data"]])), INPV_Control_SC30$membership)
colnames(INPV_Control_SC30_GE) <- paste("MC", seq(ncol(INPV_Control_SC30_GE)), sep = "")

# L4_ASD
L4_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["L4_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["L4_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
L4_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["L4_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["L4_ASD_lncRNAs_data"]])), L4_ASD_SC30$membership)
colnames(L4_ASD_SC30_GE) <- paste("MC", seq(ncol(L4_ASD_SC30_GE)), sep = "")

# L4_Control
L4_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["L4_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["L4_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
L4_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["L4_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["L4_control_lncRNAs_data"]])), L4_Control_SC30$membership)
colnames(L4_Control_SC30_GE) <- paste("MC", seq(ncol(L4_Control_SC30_GE)), sep = "")

# INSST_ASD
INSST_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["INSST_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["INSST_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
INSST_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["INSST_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["INSST_ASD_lncRNAs_data"]])), INSST_ASD_SC30$membership)
colnames(INSST_ASD_SC30_GE) <- paste("MC", seq(ncol(INSST_ASD_SC30_GE)), sep = "")

# INSST_Control
INSST_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["INSST_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["INSST_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
INSST_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["INSST_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["INSST_control_lncRNAs_data"]])), INSST_Control_SC30$membership)
colnames(INSST_Control_SC30_GE) <- paste("MC", seq(ncol(INSST_Control_SC30_GE)), sep = "")

# Neumat_ASD
Neumat_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["Neumat_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["Neumat_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Neumat_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["Neumat_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["Neumat_ASD_lncRNAs_data"]])), Neumat_ASD_SC30$membership)
colnames(Neumat_ASD_SC30_GE) <- paste("MC", seq(ncol(Neumat_ASD_SC30_GE)), sep = "")

# Neumat_Control
Neumat_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["Neumat_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["Neumat_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
Neumat_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["Neumat_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["Neumat_control_lncRNAs_data"]])), Neumat_Control_SC30$membership)
colnames(Neumat_Control_SC30_GE) <- paste("MC", seq(ncol(Neumat_Control_SC30_GE)), sep = "")

# ASTPP_ASD
ASTPP_ASD_SC30 <- SCimplify(as.matrix(rbind(ASD_celltype_mRNAs_list[["ASTPP_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["ASTPP_ASD_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
ASTPP_ASD_SC30_GE <- supercell_GE(as.matrix(rbind(ASD_celltype_mRNAs_list[["ASTPP_ASD_mRNAs_data"]], ASD_celltype_lncRNAs_list[["ASTPP_ASD_lncRNAs_data"]])), ASTPP_ASD_SC30$membership)
colnames(ASTPP_ASD_SC30_GE) <- paste("MC", seq(ncol(ASTPP_ASD_SC30_GE)), sep = "")

# ASTPP_Control
ASTPP_Control_SC30 <- SCimplify(as.matrix(rbind(Control_celltype_mRNAs_list[["ASTPP_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["ASTPP_control_lncRNAs_data"]])),  # gene expression matrix 
                      k.knn = 5, # number of nearest neighbors to build kNN network
                      gamma = 30, # graining level
                      n.var.genes = 2000 # number of the top variable genes to use for dimentionality reduction
		      )
ASTPP_Control_SC30_GE <- supercell_GE(as.matrix(rbind(Control_celltype_mRNAs_list[["ASTPP_control_mRNAs_data"]], Control_celltype_lncRNAs_list[["ASTPP_control_lncRNAs_data"]])), ASTPP_Control_SC30$membership)
colnames(ASTPP_Control_SC30_GE) <- paste("MC", seq(ncol(ASTPP_Control_SC30_GE)), sep = "")
```

## Step 2: Cell trajectory inference
```{r, eval=TRUE, include=TRUE}
# ASD and Control
ASD_space <- reduce_dimensionality(t(as.matrix(ASD_SC30_GE)), ndim =2)
Control_space <- reduce_dimensionality(t(as.matrix(Control_SC30_GE)), ndim = 2)

ASD_model <- infer_trajectory(ASD_space)
Control_model <- infer_trajectory(Control_space)

ASD_model_data <- t(as.matrix(ASD_SC30_GE))[match(names(sort(ASD_model$time)), colnames(ASD_SC30_GE)), ]
Control_model_data <- t(as.matrix(Control_SC30_GE))[match(names(sort(Control_model$time)), colnames(Control_SC30_GE)), ]

# ACC_ASD, ACC_Control, PFC_ASD, PFC_Control
ACC_ASD_space <- reduce_dimensionality(t(as.matrix(ACC_ASD_SC30_GE)), ndim =2)
ACC_Control_space <- reduce_dimensionality(t(as.matrix(ACC_Control_SC30_GE)), ndim = 2)
PFC_ASD_space <- reduce_dimensionality(t(as.matrix(PFC_ASD_SC30_GE)), ndim =2)
PFC_Control_space <- reduce_dimensionality(t(as.matrix(PFC_Control_SC30_GE)), ndim = 2)

ACC_ASD_model <- infer_trajectory(ACC_ASD_space)
ACC_Control_model <- infer_trajectory(ACC_Control_space)
PFC_ASD_model <- infer_trajectory(PFC_ASD_space)
PFC_Control_model <- infer_trajectory(PFC_Control_space)

ACC_ASD_model_data <- t(as.matrix(ACC_ASD_SC30_GE))[match(names(sort(ACC_ASD_model$time)), colnames(ACC_ASD_SC30_GE)), ]
ACC_Control_model_data <- t(as.matrix(ACC_Control_SC30_GE))[match(names(sort(ACC_Control_model$time)), colnames(ACC_Control_SC30_GE)), ]
PFC_ASD_model_data <- t(as.matrix(PFC_ASD_SC30_GE))[match(names(sort(PFC_ASD_model$time)), colnames(PFC_ASD_SC30_GE)), ]
PFC_Control_model_data <- t(as.matrix(PFC_Control_SC30_GE))[match(names(sort(PFC_Control_model$time)), colnames(PFC_Control_SC30_GE)), ]

# Lower18_ASD, Lower18_Control, Larger18_ASD, Larger18_Control
Lower18_ASD_space <- reduce_dimensionality(t(as.matrix(Lower18_ASD_SC30_GE)), ndim =2)
Lower18_Control_space <- reduce_dimensionality(t(as.matrix(Lower18_Control_SC30_GE)), ndim = 2)
Larger18_ASD_space <- reduce_dimensionality(t(as.matrix(Larger18_ASD_SC30_GE)), ndim =2)
Larger18_Control_space <- reduce_dimensionality(t(as.matrix(Larger18_Control_SC30_GE)), ndim = 2)

Lower18_ASD_model <- infer_trajectory(Lower18_ASD_space)
Lower18_Control_model <- infer_trajectory(Lower18_Control_space)
Larger18_ASD_model <- infer_trajectory(Larger18_ASD_space)
Larger18_Control_model <- infer_trajectory(Larger18_Control_space)

Lower18_ASD_model_data <- t(as.matrix(Lower18_ASD_SC30_GE))[match(names(sort(Lower18_ASD_model$time)), colnames(Lower18_ASD_SC30_GE)), ]
Lower18_Control_model_data <- t(as.matrix(Lower18_Control_SC30_GE))[match(names(sort(Lower18_Control_model$time)), colnames(Lower18_Control_SC30_GE)), ]
Larger18_ASD_model_data <- t(as.matrix(Larger18_ASD_SC30_GE))[match(names(sort(Larger18_ASD_model$time)), colnames(Larger18_ASD_SC30_GE)), ]
Larger18_Control_model_data <- t(as.matrix(Larger18_Control_SC30_GE))[match(names(sort(Larger18_Control_model$time)), colnames(Larger18_Control_SC30_GE)), ]

# Male_ASD, Male_Control, Female_ASD, Female_Control
Male_ASD_space <- reduce_dimensionality(t(as.matrix(Male_ASD_SC30_GE)), ndim =2)
Male_Control_space <- reduce_dimensionality(t(as.matrix(Male_Control_SC30_GE)), ndim = 2)
Female_ASD_space <- reduce_dimensionality(t(as.matrix(Female_ASD_SC30_GE)), ndim =2)
Female_Control_space <- reduce_dimensionality(t(as.matrix(Female_Control_SC30_GE)), ndim = 2)

Male_ASD_model <- infer_trajectory(Male_ASD_space)
Male_Control_model <- infer_trajectory(Male_Control_space)
Female_ASD_model <- infer_trajectory(Female_ASD_space)
Female_Control_model <- infer_trajectory(Female_Control_space)

Male_ASD_model_data <- t(as.matrix(Male_ASD_SC30_GE))[match(names(sort(Male_ASD_model$time)), colnames(Male_ASD_SC30_GE)), ]
Male_Control_model_data <- t(as.matrix(Male_Control_SC30_GE))[match(names(sort(Male_Control_model$time)), colnames(Male_Control_SC30_GE)), ]
Female_ASD_model_data <- t(as.matrix(Female_ASD_SC30_GE))[match(names(sort(Female_ASD_model$time)), colnames(Female_ASD_SC30_GE)), ]
Female_Control_model_data <- t(as.matrix(Female_Control_SC30_GE))[match(names(sort(Female_Control_model$time)), colnames(Female_Control_SC30_GE)), ]

# NeuNRGNII_ASD, NeuNRGNII_Control
NeuNRGNII_ASD_space <- reduce_dimensionality(t(as.matrix(NeuNRGNII_ASD_SC30_GE)), ndim =2)
NeuNRGNII_Control_space <- reduce_dimensionality(t(as.matrix(NeuNRGNII_Control_SC30_GE)), ndim = 2)

NeuNRGNII_ASD_model <- infer_trajectory(NeuNRGNII_ASD_space)
NeuNRGNII_Control_model <- infer_trajectory(NeuNRGNII_Control_space)

NeuNRGNII_ASD_model_data <- t(as.matrix(NeuNRGNII_ASD_SC30_GE))[match(names(sort(NeuNRGNII_ASD_model$time)), colnames(NeuNRGNII_ASD_SC30_GE)), ]
NeuNRGNII_Control_model_data <- t(as.matrix(NeuNRGNII_Control_SC30_GE))[match(names(sort(NeuNRGNII_Control_model$time)), colnames(NeuNRGNII_Control_SC30_GE)), ]

# L56_ASD, L56_Control
L56_ASD_space <- reduce_dimensionality(t(as.matrix(L56_ASD_SC30_GE)), ndim =2)
L56_Control_space <- reduce_dimensionality(t(as.matrix(L56_Control_SC30_GE)), ndim = 2)

L56_ASD_model <- infer_trajectory(L56_ASD_space)
L56_Control_model <- infer_trajectory(L56_Control_space)

L56_ASD_model_data <- t(as.matrix(L56_ASD_SC30_GE))[match(names(sort(L56_ASD_model$time)), colnames(L56_ASD_SC30_GE)), ]
L56_Control_model_data <- t(as.matrix(L56_Control_SC30_GE))[match(names(sort(L56_Control_model$time)), colnames(L56_Control_SC30_GE)), ]

# Oligodendrocytes_ASD, Oligodendrocytes_Control
Oligodendrocytes_ASD_space <- reduce_dimensionality(t(as.matrix(Oligodendrocytes_ASD_SC30_GE)), ndim =2)
Oligodendrocytes_Control_space <- reduce_dimensionality(t(as.matrix(Oligodendrocytes_Control_SC30_GE)), ndim = 2)

Oligodendrocytes_ASD_model <- infer_trajectory(Oligodendrocytes_ASD_space)
Oligodendrocytes_Control_model <- infer_trajectory(Oligodendrocytes_Control_space)

Oligodendrocytes_ASD_model_data <- t(as.matrix(Oligodendrocytes_ASD_SC30_GE))[match(names(sort(Oligodendrocytes_ASD_model$time)), colnames(Oligodendrocytes_ASD_SC30_GE)), ]
Oligodendrocytes_Control_model_data <- t(as.matrix(Oligodendrocytes_Control_SC30_GE))[match(names(sort(Oligodendrocytes_Control_model$time)), colnames(Oligodendrocytes_Control_SC30_GE)), ]

# OPC_ASD, OPC_Control
OPC_ASD_space <- reduce_dimensionality(t(as.matrix(OPC_ASD_SC30_GE)), ndim =2)
OPC_Control_space <- reduce_dimensionality(t(as.matrix(OPC_Control_SC30_GE)), ndim = 2)

OPC_ASD_model <- infer_trajectory(OPC_ASD_space)
OPC_Control_model <- infer_trajectory(OPC_Control_space)

OPC_ASD_model_data <- t(as.matrix(OPC_ASD_SC30_GE))[match(names(sort(OPC_ASD_model$time)), colnames(OPC_ASD_SC30_GE)), ]
OPC_Control_model_data <- t(as.matrix(OPC_Control_SC30_GE))[match(names(sort(OPC_Control_model$time)), colnames(OPC_Control_SC30_GE)), ]

# ASTFB_ASD, ASTFB_Control
ASTFB_ASD_space <- reduce_dimensionality(t(as.matrix(ASTFB_ASD_SC30_GE)), ndim =2)
ASTFB_Control_space <- reduce_dimensionality(t(as.matrix(ASTFB_Control_SC30_GE)), ndim = 2)

ASTFB_ASD_model <- infer_trajectory(ASTFB_ASD_space)
ASTFB_Control_model <- infer_trajectory(ASTFB_Control_space)

ASTFB_ASD_model_data <- t(as.matrix(ASTFB_ASD_SC30_GE))[match(names(sort(ASTFB_ASD_model$time)), colnames(ASTFB_ASD_SC30_GE)), ]
ASTFB_Control_model_data <- t(as.matrix(ASTFB_Control_SC30_GE))[match(names(sort(ASTFB_Control_model$time)), colnames(ASTFB_Control_SC30_GE)), ]

# Endothelial_ASD, Endothelial_Control
Endothelial_ASD_space <- reduce_dimensionality(t(as.matrix(Endothelial_ASD_SC30_GE)), ndim =2)
Endothelial_Control_space <- reduce_dimensionality(t(as.matrix(Endothelial_Control_SC30_GE)), ndim = 2)

Endothelial_ASD_model <- infer_trajectory(Endothelial_ASD_space)
Endothelial_Control_model <- infer_trajectory(Endothelial_Control_space)

Endothelial_ASD_model_data <- t(as.matrix(Endothelial_ASD_SC30_GE))[match(names(sort(Endothelial_ASD_model$time)), colnames(Endothelial_ASD_SC30_GE)), ]
Endothelial_Control_model_data <- t(as.matrix(Endothelial_Control_SC30_GE))[match(names(sort(Endothelial_Control_model$time)), colnames(Endothelial_Control_SC30_GE)), ]

# Microglia_ASD, Microglia_Control
Microglia_ASD_space <- reduce_dimensionality(t(as.matrix(Microglia_ASD_SC30_GE)), ndim =2)
Microglia_Control_space <- reduce_dimensionality(t(as.matrix(Microglia_Control_SC30_GE)), ndim = 2)

Microglia_ASD_model <- infer_trajectory(Microglia_ASD_space)
Microglia_Control_model <- infer_trajectory(Microglia_Control_space)

Microglia_ASD_model_data <- t(as.matrix(Microglia_ASD_SC30_GE))[match(names(sort(Microglia_ASD_model$time)), colnames(Microglia_ASD_SC30_GE)), ]
Microglia_Control_model_data <- t(as.matrix(Microglia_Control_SC30_GE))[match(names(sort(Microglia_Control_model$time)), colnames(Microglia_Control_SC30_GE)), ]

# NeuNRGNI_ASD, NeuNRGNI_Control
NeuNRGNI_ASD_space <- reduce_dimensionality(t(as.matrix(NeuNRGNI_ASD_SC30_GE)), ndim =2)
NeuNRGNI_Control_space <- reduce_dimensionality(t(as.matrix(NeuNRGNI_Control_SC30_GE)), ndim = 2)

NeuNRGNI_ASD_model <- infer_trajectory(NeuNRGNI_ASD_space)
NeuNRGNI_Control_model <- infer_trajectory(NeuNRGNI_Control_space)

NeuNRGNI_ASD_model_data <- t(as.matrix(NeuNRGNI_ASD_SC30_GE))[match(names(sort(NeuNRGNI_ASD_model$time)), colnames(NeuNRGNI_ASD_SC30_GE)), ]
NeuNRGNI_Control_model_data <- t(as.matrix(NeuNRGNI_Control_SC30_GE))[match(names(sort(NeuNRGNI_Control_model$time)), colnames(NeuNRGNI_Control_SC30_GE)), ]

# INVIP_ASD, INVIP_Control
INVIP_ASD_space <- reduce_dimensionality(t(as.matrix(INVIP_ASD_SC30_GE)), ndim =2)
INVIP_Control_space <- reduce_dimensionality(t(as.matrix(INVIP_Control_SC30_GE)), ndim = 2)

INVIP_ASD_model <- infer_trajectory(INVIP_ASD_space)
INVIP_Control_model <- infer_trajectory(INVIP_Control_space)

INVIP_ASD_model_data <- t(as.matrix(INVIP_ASD_SC30_GE))[match(names(sort(INVIP_ASD_model$time)), colnames(INVIP_ASD_SC30_GE)), ]
INVIP_Control_model_data <- t(as.matrix(INVIP_Control_SC30_GE))[match(names(sort(INVIP_Control_model$time)), colnames(INVIP_Control_SC30_GE)), ]

# L56CC_ASD, L56CC_Control
L56CC_ASD_space <- reduce_dimensionality(t(as.matrix(L56CC_ASD_SC30_GE)), ndim =2)
L56CC_Control_space <- reduce_dimensionality(t(as.matrix(L56CC_Control_SC30_GE)), ndim = 2)

L56CC_ASD_model <- infer_trajectory(L56CC_ASD_space)
L56CC_Control_model <- infer_trajectory(L56CC_Control_space)

L56CC_ASD_model_data <- t(as.matrix(L56CC_ASD_SC30_GE))[match(names(sort(L56CC_ASD_model$time)), colnames(L56CC_ASD_SC30_GE)), ]
L56CC_Control_model_data <- t(as.matrix(L56CC_Control_SC30_GE))[match(names(sort(L56CC_Control_model$time)), colnames(L56CC_Control_SC30_GE)), ]

# INSV2C_ASD, INSV2C_Control
INSV2C_ASD_space <- reduce_dimensionality(t(as.matrix(INSV2C_ASD_SC30_GE)), ndim =2)
INSV2C_Control_space <- reduce_dimensionality(t(as.matrix(INSV2C_Control_SC30_GE)), ndim = 2)

INSV2C_ASD_model <- infer_trajectory(INSV2C_ASD_space)
INSV2C_Control_model <- infer_trajectory(INSV2C_Control_space)

INSV2C_ASD_model_data <- t(as.matrix(INSV2C_ASD_SC30_GE))[match(names(sort(INSV2C_ASD_model$time)), colnames(INSV2C_ASD_SC30_GE)), ]
INSV2C_Control_model_data <- t(as.matrix(INSV2C_Control_SC30_GE))[match(names(sort(INSV2C_Control_model$time)), colnames(INSV2C_Control_SC30_GE)), ]

# L23_ASD, L23_Control
L23_ASD_space <- reduce_dimensionality(t(as.matrix(L23_ASD_SC30_GE)), ndim =2)
L23_Control_space <- reduce_dimensionality(t(as.matrix(L23_Control_SC30_GE)), ndim = 2)

L23_ASD_model <- infer_trajectory(L23_ASD_space)
L23_Control_model <- infer_trajectory(L23_Control_space)

L23_ASD_model_data <- t(as.matrix(L23_ASD_SC30_GE))[match(names(sort(L23_ASD_model$time)), colnames(L23_ASD_SC30_GE)), ]
L23_Control_model_data <- t(as.matrix(L23_Control_SC30_GE))[match(names(sort(L23_Control_model$time)), colnames(L23_Control_SC30_GE)), ]

# INPV_ASD, INPV_Control
INPV_ASD_space <- reduce_dimensionality(t(as.matrix(INPV_ASD_SC30_GE)), ndim =2)
INPV_Control_space <- reduce_dimensionality(t(as.matrix(INPV_Control_SC30_GE)), ndim = 2)

INPV_ASD_model <- infer_trajectory(INPV_ASD_space)
INPV_Control_model <- infer_trajectory(INPV_Control_space)

INPV_ASD_model_data <- t(as.matrix(INPV_ASD_SC30_GE))[match(names(sort(INPV_ASD_model$time)), colnames(INPV_ASD_SC30_GE)), ]
INPV_Control_model_data <- t(as.matrix(INPV_Control_SC30_GE))[match(names(sort(INPV_Control_model$time)), colnames(INPV_Control_SC30_GE)), ]

# L4_ASD, L4_Control
L4_ASD_space <- reduce_dimensionality(t(as.matrix(L4_ASD_SC30_GE)), ndim =2)
L4_Control_space <- reduce_dimensionality(t(as.matrix(L4_Control_SC30_GE)), ndim = 2)

L4_ASD_model <- infer_trajectory(L4_ASD_space)
L4_Control_model <- infer_trajectory(L4_Control_space)

L4_ASD_model_data <- t(as.matrix(L4_ASD_SC30_GE))[match(names(sort(L4_ASD_model$time)), colnames(L4_ASD_SC30_GE)), ]
L4_Control_model_data <- t(as.matrix(L4_Control_SC30_GE))[match(names(sort(L4_Control_model$time)), colnames(L4_Control_SC30_GE)), ]

# INSST_ASD, INSST_Control
INSST_ASD_space <- reduce_dimensionality(t(as.matrix(INSST_ASD_SC30_GE)), ndim =2)
INSST_Control_space <- reduce_dimensionality(t(as.matrix(INSST_Control_SC30_GE)), ndim = 2)

INSST_ASD_model <- infer_trajectory(INSST_ASD_space)
INSST_Control_model <- infer_trajectory(INSST_Control_space)

INSST_ASD_model_data <- t(as.matrix(INSST_ASD_SC30_GE))[match(names(sort(INSST_ASD_model$time)), colnames(INSST_ASD_SC30_GE)), ]
INSST_Control_model_data <- t(as.matrix(INSST_Control_SC30_GE))[match(names(sort(INSST_Control_model$time)), colnames(INSST_Control_SC30_GE)), ]

# Neumat_ASD, Neumat_Control
Neumat_ASD_space <- reduce_dimensionality(t(as.matrix(Neumat_ASD_SC30_GE)), ndim =2)
Neumat_Control_space <- reduce_dimensionality(t(as.matrix(Neumat_Control_SC30_GE)), ndim = 2)

Neumat_ASD_model <- infer_trajectory(Neumat_ASD_space)
Neumat_Control_model <- infer_trajectory(Neumat_Control_space)

Neumat_ASD_model_data <- t(as.matrix(Neumat_ASD_SC30_GE))[match(names(sort(Neumat_ASD_model$time)), colnames(Neumat_ASD_SC30_GE)), ]
Neumat_Control_model_data <- t(as.matrix(Neumat_Control_SC30_GE))[match(names(sort(Neumat_Control_model$time)), colnames(Neumat_Control_SC30_GE)), ]

# ASTPP_ASD, ASTPP_Control
ASTPP_ASD_space <- reduce_dimensionality(t(as.matrix(ASTPP_ASD_SC30_GE)), ndim =2)
ASTPP_Control_space <- reduce_dimensionality(t(as.matrix(ASTPP_Control_SC30_GE)), ndim = 2)

ASTPP_ASD_model <- infer_trajectory(ASTPP_ASD_space)
ASTPP_Control_model <- infer_trajectory(ASTPP_Control_space)

ASTPP_ASD_model_data <- t(as.matrix(ASTPP_ASD_SC30_GE))[match(names(sort(ASTPP_ASD_model$time)), colnames(ASTPP_ASD_SC30_GE)), ]
ASTPP_Control_model_data <- t(as.matrix(ASTPP_Control_SC30_GE))[match(names(sort(ASTPP_Control_model$time)), colnames(ASTPP_Control_SC30_GE)), ]
```

## Step 3: Causal inference using Clean
```{r, eval=TRUE, include=TRUE}
################################################################################  Clean application ############################################################################
# ASD and Control
ASD_res_darkcausality <- darkcausality_parallel(ASD_model_data, cause, effect, num.cores = 48)
Control_res_darkcausality <- darkcausality_parallel(Control_model_data, cause, effect, num.cores = 48)

# ACC_ASD, ACC_Control, PFC_ASD, PFC_Control
ACC_ASD_res_darkcausality <- darkcausality_parallel(ACC_ASD_model_data, cause, effect, num.cores = 48)
ACC_Control_res_darkcausality <- darkcausality_parallel(ACC_Control_model_data, cause, effect, num.cores = 48)
PFC_ASD_res_darkcausality <- darkcausality_parallel(PFC_ASD_model_data, cause, effect, num.cores = 48)
PFC_Control_res_darkcausality <- darkcausality_parallel(PFC_Control_model_data, cause, effect, num.cores = 48)

# Lower18_ASD, Lower18_Control, Larger18_ASD, Larger18_Control
Lower18_ASD_res_darkcausality <- darkcausality_parallel(Lower18_ASD_model_data, cause, effect, num.cores = 48)
Lower18_Control_res_darkcausality <- darkcausality_parallel(Lower18_Control_model_data, cause, effect, num.cores = 48)
Larger18_ASD_res_darkcausality <- darkcausality_parallel(Larger18_ASD_model_data, cause, effect, num.cores = 48)
Larger18_Control_res_darkcausality <- darkcausality_parallel(Larger18_Control_model_data, cause, effect, num.cores = 48)

# Male_ASD, Male_Control, Female_ASD, Female_Control
Male_ASD_res_darkcausality <- darkcausality_parallel(Male_ASD_model_data, cause, effect, num.cores = 48)
Male_Control_res_darkcausality <- darkcausality_parallel(Male_Control_model_data, cause, effect, num.cores = 48)
Female_ASD_res_darkcausality <- darkcausality_parallel(Female_ASD_model_data, cause, effect, num.cores = 48)
Female_Control_res_darkcausality <- darkcausality_parallel(Female_Control_model_data, cause, effect, num.cores = 48)

# NeuNRGNII_ASD, NeuNRGNII_Control
NeuNRGNII_ASD_res_darkcausality <- darkcausality_parallel(NeuNRGNII_ASD_model_data, cause, effect, num.cores = 48)
NeuNRGNII_Control_res_darkcausality <- darkcausality_parallel(NeuNRGNII_Control_model_data, cause, effect, num.cores = 48)

# L56_ASD, L56_Control
L56_ASD_res_darkcausality <- darkcausality_parallel(L56_ASD_model_data, cause, effect, num.cores = 48)
L56_Control_res_darkcausality <- darkcausality_parallel(L56_Control_model_data, cause, effect, num.cores = 48)

# Oligodendrocytes_ASD, Oligodendrocytes_Control
Oligodendrocytes_ASD_res_darkcausality <- darkcausality_parallel(Oligodendrocytes_ASD_model_data, cause, effect, num.cores = 48)
Oligodendrocytes_Control_res_darkcausality <- darkcausality_parallel(Oligodendrocytes_Control_model_data, cause, effect, num.cores = 48)

# OPC_ASD, OPC_Control
OPC_ASD_res_darkcausality <- darkcausality_parallel(OPC_ASD_model_data, cause, effect, num.cores = 48)
OPC_Control_res_darkcausality <- darkcausality_parallel(OPC_Control_model_data, cause, effect, num.cores = 48)
 
# ASTFB_ASD, ASTFB_Control
ASTFB_ASD_res_darkcausality <- darkcausality_parallel(ASTFB_ASD_model_data, cause, effect, num.cores = 48)
ASTFB_Control_res_darkcausality <- darkcausality_parallel(ASTFB_Control_model_data, cause, effect, num.cores = 48)

# Endothelial_ASD, Endothelial_Control
Endothelial_ASD_res_darkcausality <- darkcausality_parallel(Endothelial_ASD_model_data, cause, effect, num.cores = 48)
Endothelial_Control_res_darkcausality <- darkcausality_parallel(Endothelial_Control_model_data, cause, effect, num.cores = 48)

# Microglia_ASD, Microglia_Control
Microglia_ASD_res_darkcausality <- darkcausality_parallel(Microglia_ASD_model_data, cause, effect, num.cores = 48)
Microglia_Control_res_darkcausality <- darkcausality_parallel(Microglia_Control_model_data, cause, effect, num.cores = 48)

# NeuNRGNI_ASD, NeuNRGNI_Control
NeuNRGNI_ASD_res_darkcausality <- darkcausality_parallel(NeuNRGNI_ASD_model_data, cause, effect, num.cores = 48)
NeuNRGNI_Control_res_darkcausality <- darkcausality_parallel(NeuNRGNI_Control_model_data, cause, effect, num.cores = 48)

# INVIP_ASD, INVIP_Control
INVIP_ASD_res_darkcausality <- darkcausality_parallel(INVIP_ASD_model_data, cause, effect, num.cores = 48)
INVIP_Control_res_darkcausality <- darkcausality_parallel(INVIP_Control_model_data, cause, effect, num.cores = 48)

# L56CC_ASD, L56CC_Control
L56CC_ASD_res_darkcausality <- darkcausality_parallel(L56CC_ASD_model_data, cause, effect, num.cores = 48)
L56CC_Control_res_darkcausality <- darkcausality_parallel(L56CC_Control_model_data, cause, effect, num.cores = 48)

# INSV2C_ASD, INSV2C_Control
INSV2C_ASD_res_darkcausality <- darkcausality_parallel(INSV2C_ASD_model_data, cause, effect, num.cores = 48)
INSV2C_Control_res_darkcausality <- darkcausality_parallel(INSV2C_Control_model_data, cause, effect, num.cores = 48)

# L23_ASD, L23_Control
L23_ASD_res_darkcausality <- darkcausality_parallel(L23_ASD_model_data, cause, effect, num.cores = 48)
L23_Control_res_darkcausality <- darkcausality_parallel(L23_Control_model_data, cause, effect, num.cores = 48)

# INPV_ASD, INPV_Control
INPV_ASD_res_darkcausality <- darkcausality_parallel(INPV_ASD_model_data, cause, effect, num.cores = 48)
INPV_Control_res_darkcausality <- darkcausality_parallel(INPV_Control_model_data, cause, effect, num.cores = 48)

# L4_ASD, L4_Control
L4_ASD_res_darkcausality <- darkcausality_parallel(L4_ASD_model_data, cause, effect, num.cores = 48)
L4_Control_res_darkcausality <- darkcausality_parallel(L4_Control_model_data, cause, effect, num.cores = 48)

# INSST_ASD, INSST_Control
INSST_ASD_res_darkcausality <- darkcausality_parallel(INSST_ASD_model_data, cause, effect, num.cores = 48)
INSST_Control_res_darkcausality <- darkcausality_parallel(INSST_Control_model_data, cause, effect, num.cores = 48)

# Neumat_ASD, Neumat_Control
Neumat_ASD_res_darkcausality <- darkcausality_parallel(Neumat_ASD_model_data, cause, effect, num.cores = 48)
Neumat_Control_res_darkcausality <- darkcausality_parallel(Neumat_Control_model_data, cause, effect, num.cores = 48)

# ASTPP_ASD, ASTPP_Control
ASTPP_ASD_res_darkcausality <- darkcausality_parallel(ASTPP_ASD_model_data, cause, effect, num.cores = 48)
ASTPP_Control_res_darkcausality <- darkcausality_parallel(ASTPP_Control_model_data, cause, effect, num.cores = 48)

# ASD and Control
ASD_res_darkcausality[[2]] <- ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
ASD_res_darkcausality[[3]] <- ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
ASD_res_darkcausality[[4]] <- ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
ASD_res_darkcausality_sig <- sigPC(ASD_res_darkcausality[[2]], ASD_res_darkcausality[[3]], ASD_res_darkcausality[[4]])
Control_res_darkcausality[[2]] <- Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Control_res_darkcausality[[3]] <- Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Control_res_darkcausality[[4]] <- Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Control_res_darkcausality_sig <- sigPC(Control_res_darkcausality[[2]], Control_res_darkcausality[[3]], Control_res_darkcausality[[4]])
ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(ASD_res_darkcausality_sig[[1]] + ASD_res_darkcausality_sig[[2]] + ASD_res_darkcausality_sig[[3]]))
Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Control_res_darkcausality_sig[[1]] + Control_res_darkcausality_sig[[2]] + Control_res_darkcausality_sig[[3]]))

# ACC_ASD, ACC_Control, PFC_ASD, PFC_Control
ACC_ASD_res_darkcausality[[2]] <- ACC_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
ACC_ASD_res_darkcausality[[3]] <- ACC_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
ACC_ASD_res_darkcausality[[4]] <- ACC_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
ACC_ASD_res_darkcausality_sig <- sigPC(ACC_ASD_res_darkcausality[[2]], ACC_ASD_res_darkcausality[[3]], ACC_ASD_res_darkcausality[[4]])
ACC_Control_res_darkcausality[[2]] <- ACC_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
ACC_Control_res_darkcausality[[3]] <- ACC_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
ACC_Control_res_darkcausality[[4]] <- ACC_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
ACC_Control_res_darkcausality_sig <- sigPC(ACC_Control_res_darkcausality[[2]], ACC_Control_res_darkcausality[[3]], ACC_Control_res_darkcausality[[4]])
PFC_ASD_res_darkcausality[[2]] <- PFC_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
PFC_ASD_res_darkcausality[[3]] <- PFC_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
PFC_ASD_res_darkcausality[[4]] <- PFC_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
PFC_ASD_res_darkcausality_sig <- sigPC(PFC_ASD_res_darkcausality[[2]], PFC_ASD_res_darkcausality[[3]], PFC_ASD_res_darkcausality[[4]])
PFC_Control_res_darkcausality[[2]] <- PFC_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
PFC_Control_res_darkcausality[[3]] <- PFC_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
PFC_Control_res_darkcausality[[4]] <- PFC_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
PFC_Control_res_darkcausality_sig <- sigPC(PFC_Control_res_darkcausality[[2]], PFC_Control_res_darkcausality[[3]], PFC_Control_res_darkcausality[[4]])
ACC_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(ACC_ASD_res_darkcausality_sig[[1]] + ACC_ASD_res_darkcausality_sig[[2]] + ACC_ASD_res_darkcausality_sig[[3]]))
ACC_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(ACC_Control_res_darkcausality_sig[[1]] + ACC_Control_res_darkcausality_sig[[2]] + ACC_Control_res_darkcausality_sig[[3]]))
PFC_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(PFC_ASD_res_darkcausality_sig[[1]] + PFC_ASD_res_darkcausality_sig[[2]] + PFC_ASD_res_darkcausality_sig[[3]]))
PFC_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(PFC_Control_res_darkcausality_sig[[1]] + PFC_Control_res_darkcausality_sig[[2]] + PFC_Control_res_darkcausality_sig[[3]]))

# Lower18_ASD, Lower18_Control, Larger18_ASD, Larger18_Control
Lower18_ASD_res_darkcausality[[2]] <- Lower18_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Lower18_ASD_res_darkcausality[[3]] <- Lower18_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Lower18_ASD_res_darkcausality[[4]] <- Lower18_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Lower18_ASD_res_darkcausality_sig <- sigPC(Lower18_ASD_res_darkcausality[[2]], Lower18_ASD_res_darkcausality[[3]], Lower18_ASD_res_darkcausality[[4]])
Lower18_Control_res_darkcausality[[2]] <- Lower18_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Lower18_Control_res_darkcausality[[3]] <- Lower18_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Lower18_Control_res_darkcausality[[4]] <- Lower18_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Lower18_Control_res_darkcausality_sig <- sigPC(Lower18_Control_res_darkcausality[[2]], Lower18_Control_res_darkcausality[[3]], Lower18_Control_res_darkcausality[[4]])
Larger18_ASD_res_darkcausality[[2]] <- Larger18_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Larger18_ASD_res_darkcausality[[3]] <- Larger18_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Larger18_ASD_res_darkcausality[[4]] <- Larger18_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Larger18_ASD_res_darkcausality_sig <- sigPC(Larger18_ASD_res_darkcausality[[2]], Larger18_ASD_res_darkcausality[[3]], Larger18_ASD_res_darkcausality[[4]])
Larger18_Control_res_darkcausality[[2]] <- Larger18_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Larger18_Control_res_darkcausality[[3]] <- Larger18_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Larger18_Control_res_darkcausality[[4]] <- Larger18_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Larger18_Control_res_darkcausality_sig <- sigPC(Larger18_Control_res_darkcausality[[2]], Larger18_Control_res_darkcausality[[3]], Larger18_Control_res_darkcausality[[4]])
Lower18_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Lower18_ASD_res_darkcausality_sig[[1]] + Lower18_ASD_res_darkcausality_sig[[2]] + Lower18_ASD_res_darkcausality_sig[[3]]))
Lower18_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Lower18_Control_res_darkcausality_sig[[1]] + Lower18_Control_res_darkcausality_sig[[2]] + Lower18_Control_res_darkcausality_sig[[3]]))
Larger18_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Larger18_ASD_res_darkcausality_sig[[1]] + Larger18_ASD_res_darkcausality_sig[[2]] + Larger18_ASD_res_darkcausality_sig[[3]]))
Larger18_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Larger18_Control_res_darkcausality_sig[[1]] + Larger18_Control_res_darkcausality_sig[[2]] + Larger18_Control_res_darkcausality_sig[[3]]))

# Male_ASD, Male_Control, Female_ASD, Female_Control
Male_ASD_res_darkcausality[[2]] <- Male_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Male_ASD_res_darkcausality[[3]] <- Male_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Male_ASD_res_darkcausality[[4]] <- Male_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Male_ASD_res_darkcausality_sig <- sigPC(Male_ASD_res_darkcausality[[2]], Male_ASD_res_darkcausality[[3]], Male_ASD_res_darkcausality[[4]])
Male_Control_res_darkcausality[[2]] <- Male_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Male_Control_res_darkcausality[[3]] <- Male_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Male_Control_res_darkcausality[[4]] <- Male_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Male_Control_res_darkcausality_sig <- sigPC(Male_Control_res_darkcausality[[2]], Male_Control_res_darkcausality[[3]], Male_Control_res_darkcausality[[4]])
Female_ASD_res_darkcausality[[2]] <- Female_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Female_ASD_res_darkcausality[[3]] <- Female_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Female_ASD_res_darkcausality[[4]] <- Female_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Female_ASD_res_darkcausality_sig <- sigPC(Female_ASD_res_darkcausality[[2]], Female_ASD_res_darkcausality[[3]], Female_ASD_res_darkcausality[[4]])
Female_Control_res_darkcausality[[2]] <- Female_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Female_Control_res_darkcausality[[3]] <- Female_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Female_Control_res_darkcausality[[4]] <- Female_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Female_Control_res_darkcausality_sig <- sigPC(Female_Control_res_darkcausality[[2]], Female_Control_res_darkcausality[[3]], Female_Control_res_darkcausality[[4]])
Male_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Male_ASD_res_darkcausality_sig[[1]] + Male_ASD_res_darkcausality_sig[[2]] + Male_ASD_res_darkcausality_sig[[3]]))
Male_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Male_Control_res_darkcausality_sig[[1]] + Male_Control_res_darkcausality_sig[[2]] + Male_Control_res_darkcausality_sig[[3]]))
Female_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Female_ASD_res_darkcausality_sig[[1]] + Female_ASD_res_darkcausality_sig[[2]] + Female_ASD_res_darkcausality_sig[[3]]))
Female_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Female_Control_res_darkcausality_sig[[1]] + Female_Control_res_darkcausality_sig[[2]] + Female_Control_res_darkcausality_sig[[3]]))

# NeuNRGNII_ASD, NeuNRGNII_Control
NeuNRGNII_ASD_res_darkcausality[[2]] <- NeuNRGNII_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
NeuNRGNII_ASD_res_darkcausality[[3]] <- NeuNRGNII_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
NeuNRGNII_ASD_res_darkcausality[[4]] <- NeuNRGNII_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
NeuNRGNII_ASD_res_darkcausality_sig <- sigPC(NeuNRGNII_ASD_res_darkcausality[[2]], NeuNRGNII_ASD_res_darkcausality[[3]], NeuNRGNII_ASD_res_darkcausality[[4]])
NeuNRGNII_Control_res_darkcausality[[2]] <- NeuNRGNII_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
NeuNRGNII_Control_res_darkcausality[[3]] <- NeuNRGNII_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
NeuNRGNII_Control_res_darkcausality[[4]] <- NeuNRGNII_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
NeuNRGNII_Control_res_darkcausality_sig <- sigPC(NeuNRGNII_Control_res_darkcausality[[2]], NeuNRGNII_Control_res_darkcausality[[3]], NeuNRGNII_Control_res_darkcausality[[4]])
NeuNRGNII_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(NeuNRGNII_ASD_res_darkcausality_sig[[1]] + NeuNRGNII_ASD_res_darkcausality_sig[[2]] + NeuNRGNII_ASD_res_darkcausality_sig[[3]]))
NeuNRGNII_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(NeuNRGNII_Control_res_darkcausality_sig[[1]] + NeuNRGNII_Control_res_darkcausality_sig[[2]] + NeuNRGNII_Control_res_darkcausality_sig[[3]]))

# L56_ASD, L56_Control
L56_ASD_res_darkcausality[[2]] <- L56_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
L56_ASD_res_darkcausality[[3]] <- L56_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
L56_ASD_res_darkcausality[[4]] <- L56_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
L56_ASD_res_darkcausality_sig <- sigPC(L56_ASD_res_darkcausality[[2]], L56_ASD_res_darkcausality[[3]], L56_ASD_res_darkcausality[[4]])
L56_Control_res_darkcausality[[2]] <- L56_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
L56_Control_res_darkcausality[[3]] <- L56_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
L56_Control_res_darkcausality[[4]] <- L56_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
L56_Control_res_darkcausality_sig <- sigPC(L56_Control_res_darkcausality[[2]], L56_Control_res_darkcausality[[3]], L56_Control_res_darkcausality[[4]])
L56_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(L56_ASD_res_darkcausality_sig[[1]] + L56_ASD_res_darkcausality_sig[[2]] + L56_ASD_res_darkcausality_sig[[3]]))
L56_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(L56_Control_res_darkcausality_sig[[1]] + L56_Control_res_darkcausality_sig[[2]] + L56_Control_res_darkcausality_sig[[3]]))

# Oligodendrocytes_ASD, Oligodendrocytes_Control
Oligodendrocytes_ASD_res_darkcausality[[2]] <- Oligodendrocytes_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Oligodendrocytes_ASD_res_darkcausality[[3]] <- Oligodendrocytes_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Oligodendrocytes_ASD_res_darkcausality[[4]] <- Oligodendrocytes_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Oligodendrocytes_ASD_res_darkcausality_sig <- sigPC(Oligodendrocytes_ASD_res_darkcausality[[2]], Oligodendrocytes_ASD_res_darkcausality[[3]], Oligodendrocytes_ASD_res_darkcausality[[4]])
Oligodendrocytes_Control_res_darkcausality[[2]] <- Oligodendrocytes_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Oligodendrocytes_Control_res_darkcausality[[3]] <- Oligodendrocytes_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Oligodendrocytes_Control_res_darkcausality[[4]] <- Oligodendrocytes_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Oligodendrocytes_Control_res_darkcausality_sig <- sigPC(Oligodendrocytes_Control_res_darkcausality[[2]], Oligodendrocytes_Control_res_darkcausality[[3]], Oligodendrocytes_Control_res_darkcausality[[4]])
Oligodendrocytes_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Oligodendrocytes_ASD_res_darkcausality_sig[[1]] + Oligodendrocytes_ASD_res_darkcausality_sig[[2]] + Oligodendrocytes_ASD_res_darkcausality_sig[[3]]))
Oligodendrocytes_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Oligodendrocytes_Control_res_darkcausality_sig[[1]] + Oligodendrocytes_Control_res_darkcausality_sig[[2]] + Oligodendrocytes_Control_res_darkcausality_sig[[3]]))

# OPC_ASD, OPC_Control
OPC_ASD_res_darkcausality[[2]] <- OPC_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
OPC_ASD_res_darkcausality[[3]] <- OPC_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
OPC_ASD_res_darkcausality[[4]] <- OPC_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
OPC_ASD_res_darkcausality_sig <- sigPC(OPC_ASD_res_darkcausality[[2]], OPC_ASD_res_darkcausality[[3]], OPC_ASD_res_darkcausality[[4]])
OPC_Control_res_darkcausality[[2]] <- OPC_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
OPC_Control_res_darkcausality[[3]] <- OPC_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
OPC_Control_res_darkcausality[[4]] <- OPC_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
OPC_Control_res_darkcausality_sig <- sigPC(OPC_Control_res_darkcausality[[2]], OPC_Control_res_darkcausality[[3]], OPC_Control_res_darkcausality[[4]])
OPC_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(OPC_ASD_res_darkcausality_sig[[1]] + OPC_ASD_res_darkcausality_sig[[2]] + OPC_ASD_res_darkcausality_sig[[3]]))
OPC_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(OPC_Control_res_darkcausality_sig[[1]] + OPC_Control_res_darkcausality_sig[[2]] + OPC_Control_res_darkcausality_sig[[3]]))

# ASTFB_ASD, ASTFB_Control
ASTFB_ASD_res_darkcausality[[2]] <- ASTFB_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
ASTFB_ASD_res_darkcausality[[3]] <- ASTFB_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
ASTFB_ASD_res_darkcausality[[4]] <- ASTFB_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
ASTFB_ASD_res_darkcausality_sig <- sigPC(ASTFB_ASD_res_darkcausality[[2]], ASTFB_ASD_res_darkcausality[[3]], ASTFB_ASD_res_darkcausality[[4]])
ASTFB_Control_res_darkcausality[[2]] <- ASTFB_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
ASTFB_Control_res_darkcausality[[3]] <- ASTFB_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
ASTFB_Control_res_darkcausality[[4]] <- ASTFB_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
ASTFB_Control_res_darkcausality_sig <- sigPC(ASTFB_Control_res_darkcausality[[2]], ASTFB_Control_res_darkcausality[[3]], ASTFB_Control_res_darkcausality[[4]])
ASTFB_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(ASTFB_ASD_res_darkcausality_sig[[1]] + ASTFB_ASD_res_darkcausality_sig[[2]] + ASTFB_ASD_res_darkcausality_sig[[3]]))
ASTFB_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(ASTFB_Control_res_darkcausality_sig[[1]] + ASTFB_Control_res_darkcausality_sig[[2]] + ASTFB_Control_res_darkcausality_sig[[3]]))

# Endothelial_ASD, Endothelial_Control
Endothelial_ASD_res_darkcausality[[2]] <- Endothelial_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Endothelial_ASD_res_darkcausality[[3]] <- Endothelial_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Endothelial_ASD_res_darkcausality[[4]] <- Endothelial_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Endothelial_ASD_res_darkcausality_sig <- sigPC(Endothelial_ASD_res_darkcausality[[2]], Endothelial_ASD_res_darkcausality[[3]], Endothelial_ASD_res_darkcausality[[4]])
Endothelial_Control_res_darkcausality[[2]] <- Endothelial_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Endothelial_Control_res_darkcausality[[3]] <- Endothelial_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Endothelial_Control_res_darkcausality[[4]] <- Endothelial_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Endothelial_Control_res_darkcausality_sig <- sigPC(Endothelial_Control_res_darkcausality[[2]], Endothelial_Control_res_darkcausality[[3]], Endothelial_Control_res_darkcausality[[4]])
Endothelial_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Endothelial_ASD_res_darkcausality_sig[[1]] + Endothelial_ASD_res_darkcausality_sig[[2]] + Endothelial_ASD_res_darkcausality_sig[[3]]))
Endothelial_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Endothelial_Control_res_darkcausality_sig[[1]] + Endothelial_Control_res_darkcausality_sig[[2]] + Endothelial_Control_res_darkcausality_sig[[3]]))

# Microglia_ASD, Microglia_Control
Microglia_ASD_res_darkcausality[[2]] <- Microglia_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Microglia_ASD_res_darkcausality[[3]] <- Microglia_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Microglia_ASD_res_darkcausality[[4]] <- Microglia_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Microglia_ASD_res_darkcausality_sig <- sigPC(Microglia_ASD_res_darkcausality[[2]], Microglia_ASD_res_darkcausality[[3]], Microglia_ASD_res_darkcausality[[4]])
Microglia_Control_res_darkcausality[[2]] <- Microglia_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Microglia_Control_res_darkcausality[[3]] <- Microglia_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Microglia_Control_res_darkcausality[[4]] <- Microglia_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Microglia_Control_res_darkcausality_sig <- sigPC(Microglia_Control_res_darkcausality[[2]], Microglia_Control_res_darkcausality[[3]], Microglia_Control_res_darkcausality[[4]])
Microglia_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Microglia_ASD_res_darkcausality_sig[[1]] + Microglia_ASD_res_darkcausality_sig[[2]] + Microglia_ASD_res_darkcausality_sig[[3]]))
Microglia_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Microglia_Control_res_darkcausality_sig[[1]] + Microglia_Control_res_darkcausality_sig[[2]] + Microglia_Control_res_darkcausality_sig[[3]]))

# NeuNRGNI_ASD, NeuNRGNI_Control
NeuNRGNI_ASD_res_darkcausality[[2]] <- NeuNRGNI_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
NeuNRGNI_ASD_res_darkcausality[[3]] <- NeuNRGNI_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
NeuNRGNI_ASD_res_darkcausality[[4]] <- NeuNRGNI_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
NeuNRGNI_ASD_res_darkcausality_sig <- sigPC(NeuNRGNI_ASD_res_darkcausality[[2]], NeuNRGNI_ASD_res_darkcausality[[3]], NeuNRGNI_ASD_res_darkcausality[[4]])
NeuNRGNI_Control_res_darkcausality[[2]] <- NeuNRGNI_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
NeuNRGNI_Control_res_darkcausality[[3]] <- NeuNRGNI_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
NeuNRGNI_Control_res_darkcausality[[4]] <- NeuNRGNI_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
NeuNRGNI_Control_res_darkcausality_sig <- sigPC(NeuNRGNI_Control_res_darkcausality[[2]], NeuNRGNI_Control_res_darkcausality[[3]], NeuNRGNI_Control_res_darkcausality[[4]])
NeuNRGNI_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(NeuNRGNI_ASD_res_darkcausality_sig[[1]] + NeuNRGNI_ASD_res_darkcausality_sig[[2]] + NeuNRGNI_ASD_res_darkcausality_sig[[3]]))
NeuNRGNI_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(NeuNRGNI_Control_res_darkcausality_sig[[1]] + NeuNRGNI_Control_res_darkcausality_sig[[2]] + NeuNRGNI_Control_res_darkcausality_sig[[3]]))

# INVIP_ASD, INVIP_Control
INVIP_ASD_res_darkcausality[[2]] <- INVIP_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
INVIP_ASD_res_darkcausality[[3]] <- INVIP_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
INVIP_ASD_res_darkcausality[[4]] <- INVIP_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
INVIP_ASD_res_darkcausality_sig <- sigPC(INVIP_ASD_res_darkcausality[[2]], INVIP_ASD_res_darkcausality[[3]], INVIP_ASD_res_darkcausality[[4]])
INVIP_Control_res_darkcausality[[2]] <- INVIP_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
INVIP_Control_res_darkcausality[[3]] <- INVIP_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
INVIP_Control_res_darkcausality[[4]] <- INVIP_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
INVIP_Control_res_darkcausality_sig <- sigPC(INVIP_Control_res_darkcausality[[2]], INVIP_Control_res_darkcausality[[3]], INVIP_Control_res_darkcausality[[4]])
INVIP_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(INVIP_ASD_res_darkcausality_sig[[1]] + INVIP_ASD_res_darkcausality_sig[[2]] + INVIP_ASD_res_darkcausality_sig[[3]]))
INVIP_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(INVIP_Control_res_darkcausality_sig[[1]] + INVIP_Control_res_darkcausality_sig[[2]] + INVIP_Control_res_darkcausality_sig[[3]]))

# L56CC_ASD, L56CC_Control
L56CC_ASD_res_darkcausality[[2]] <- L56CC_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
L56CC_ASD_res_darkcausality[[3]] <- L56CC_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
L56CC_ASD_res_darkcausality[[4]] <- L56CC_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
L56CC_ASD_res_darkcausality_sig <- sigPC(L56CC_ASD_res_darkcausality[[2]], L56CC_ASD_res_darkcausality[[3]], L56CC_ASD_res_darkcausality[[4]])
L56CC_Control_res_darkcausality[[2]] <- L56CC_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
L56CC_Control_res_darkcausality[[3]] <- L56CC_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
L56CC_Control_res_darkcausality[[4]] <- L56CC_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
L56CC_Control_res_darkcausality_sig <- sigPC(L56CC_Control_res_darkcausality[[2]], L56CC_Control_res_darkcausality[[3]], L56CC_Control_res_darkcausality[[4]])
L56CC_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(L56CC_ASD_res_darkcausality_sig[[1]] + L56CC_ASD_res_darkcausality_sig[[2]] + L56CC_ASD_res_darkcausality_sig[[3]]))
L56CC_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(L56CC_Control_res_darkcausality_sig[[1]] + L56CC_Control_res_darkcausality_sig[[2]] + L56CC_Control_res_darkcausality_sig[[3]]))

# INSV2C_ASD, INSV2C_Control
INSV2C_ASD_res_darkcausality[[2]] <- INSV2C_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
INSV2C_ASD_res_darkcausality[[3]] <- INSV2C_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
INSV2C_ASD_res_darkcausality[[4]] <- INSV2C_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
INSV2C_ASD_res_darkcausality_sig <- sigPC(INSV2C_ASD_res_darkcausality[[2]], INSV2C_ASD_res_darkcausality[[3]], INSV2C_ASD_res_darkcausality[[4]])
INSV2C_Control_res_darkcausality[[2]] <- INSV2C_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
INSV2C_Control_res_darkcausality[[3]] <- INSV2C_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
INSV2C_Control_res_darkcausality[[4]] <- INSV2C_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
INSV2C_Control_res_darkcausality_sig <- sigPC(INSV2C_Control_res_darkcausality[[2]], INSV2C_Control_res_darkcausality[[3]], INSV2C_Control_res_darkcausality[[4]])
INSV2C_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(INSV2C_ASD_res_darkcausality_sig[[1]] + INSV2C_ASD_res_darkcausality_sig[[2]] + INSV2C_ASD_res_darkcausality_sig[[3]]))
INSV2C_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(INSV2C_Control_res_darkcausality_sig[[1]] + INSV2C_Control_res_darkcausality_sig[[2]] + INSV2C_Control_res_darkcausality_sig[[3]]))

# L23_ASD, L23_Control
L23_ASD_res_darkcausality[[2]] <- L23_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
L23_ASD_res_darkcausality[[3]] <- L23_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
L23_ASD_res_darkcausality[[4]] <- L23_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
L23_ASD_res_darkcausality_sig <- sigPC(L23_ASD_res_darkcausality[[2]], L23_ASD_res_darkcausality[[3]], L23_ASD_res_darkcausality[[4]])
L23_Control_res_darkcausality[[2]] <- L23_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
L23_Control_res_darkcausality[[3]] <- L23_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
L23_Control_res_darkcausality[[4]] <- L23_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
L23_Control_res_darkcausality_sig <- sigPC(L23_Control_res_darkcausality[[2]], L23_Control_res_darkcausality[[3]], L23_Control_res_darkcausality[[4]])
L23_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(L23_ASD_res_darkcausality_sig[[1]] + L23_ASD_res_darkcausality_sig[[2]] + L23_ASD_res_darkcausality_sig[[3]]))
L23_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(L23_Control_res_darkcausality_sig[[1]] + L23_Control_res_darkcausality_sig[[2]] + L23_Control_res_darkcausality_sig[[3]]))

# INPV_ASD, INPV_Control
INPV_ASD_res_darkcausality[[2]] <- INPV_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
INPV_ASD_res_darkcausality[[3]] <- INPV_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
INPV_ASD_res_darkcausality[[4]] <- INPV_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
INPV_ASD_res_darkcausality_sig <- sigPC(INPV_ASD_res_darkcausality[[2]], INPV_ASD_res_darkcausality[[3]], INPV_ASD_res_darkcausality[[4]])
INPV_Control_res_darkcausality[[2]] <- INPV_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
INPV_Control_res_darkcausality[[3]] <- INPV_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
INPV_Control_res_darkcausality[[4]] <- INPV_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
INPV_Control_res_darkcausality_sig <- sigPC(INPV_Control_res_darkcausality[[2]], INPV_Control_res_darkcausality[[3]], INPV_Control_res_darkcausality[[4]])
INPV_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(INPV_ASD_res_darkcausality_sig[[1]] + INPV_ASD_res_darkcausality_sig[[2]] + INPV_ASD_res_darkcausality_sig[[3]]))
INPV_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(INPV_Control_res_darkcausality_sig[[1]] + INPV_Control_res_darkcausality_sig[[2]] + INPV_Control_res_darkcausality_sig[[3]]))

# L4_ASD, L4_Control
L4_ASD_res_darkcausality[[2]] <- L4_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
L4_ASD_res_darkcausality[[3]] <- L4_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
L4_ASD_res_darkcausality[[4]] <- L4_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
L4_ASD_res_darkcausality_sig <- sigPC(L4_ASD_res_darkcausality[[2]], L4_ASD_res_darkcausality[[3]], L4_ASD_res_darkcausality[[4]])
L4_Control_res_darkcausality[[2]] <- L4_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
L4_Control_res_darkcausality[[3]] <- L4_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
L4_Control_res_darkcausality[[4]] <- L4_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
L4_Control_res_darkcausality_sig <- sigPC(L4_Control_res_darkcausality[[2]], L4_Control_res_darkcausality[[3]], L4_Control_res_darkcausality[[4]])
L4_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(L4_ASD_res_darkcausality_sig[[1]] + L4_ASD_res_darkcausality_sig[[2]] + L4_ASD_res_darkcausality_sig[[3]]))
L4_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(L4_Control_res_darkcausality_sig[[1]] + L4_Control_res_darkcausality_sig[[2]] + L4_Control_res_darkcausality_sig[[3]]))

# INSST_ASD, INSST_Control
INSST_ASD_res_darkcausality[[2]] <- INSST_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
INSST_ASD_res_darkcausality[[3]] <- INSST_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
INSST_ASD_res_darkcausality[[4]] <- INSST_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
INSST_ASD_res_darkcausality_sig <- sigPC(INSST_ASD_res_darkcausality[[2]], INSST_ASD_res_darkcausality[[3]], INSST_ASD_res_darkcausality[[4]])
INSST_Control_res_darkcausality[[2]] <- INSST_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
INSST_Control_res_darkcausality[[3]] <- INSST_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
INSST_Control_res_darkcausality[[4]] <- INSST_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
INSST_Control_res_darkcausality_sig <- sigPC(INSST_Control_res_darkcausality[[2]], INSST_Control_res_darkcausality[[3]], INSST_Control_res_darkcausality[[4]])
INSST_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(INSST_ASD_res_darkcausality_sig[[1]] + INSST_ASD_res_darkcausality_sig[[2]] + INSST_ASD_res_darkcausality_sig[[3]]))
INSST_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(INSST_Control_res_darkcausality_sig[[1]] + INSST_Control_res_darkcausality_sig[[2]] + INSST_Control_res_darkcausality_sig[[3]]))

# Neumat_ASD, Neumat_Control
Neumat_ASD_res_darkcausality[[2]] <- Neumat_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Neumat_ASD_res_darkcausality[[3]] <- Neumat_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Neumat_ASD_res_darkcausality[[4]] <- Neumat_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Neumat_ASD_res_darkcausality_sig <- sigPC(Neumat_ASD_res_darkcausality[[2]], Neumat_ASD_res_darkcausality[[3]], Neumat_ASD_res_darkcausality[[4]])
Neumat_Control_res_darkcausality[[2]] <- Neumat_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
Neumat_Control_res_darkcausality[[3]] <- Neumat_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
Neumat_Control_res_darkcausality[[4]] <- Neumat_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
Neumat_Control_res_darkcausality_sig <- sigPC(Neumat_Control_res_darkcausality[[2]], Neumat_Control_res_darkcausality[[3]], Neumat_Control_res_darkcausality[[4]])
Neumat_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Neumat_ASD_res_darkcausality_sig[[1]] + Neumat_ASD_res_darkcausality_sig[[2]] + Neumat_ASD_res_darkcausality_sig[[3]]))
Neumat_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(Neumat_Control_res_darkcausality_sig[[1]] + Neumat_Control_res_darkcausality_sig[[2]] + Neumat_Control_res_darkcausality_sig[[3]]))

# ASTPP_ASD, ASTPP_Control
ASTPP_ASD_res_darkcausality[[2]] <- ASTPP_ASD_res_darkcausality[[2]] %>% replace(is.na(.), 0)
ASTPP_ASD_res_darkcausality[[3]] <- ASTPP_ASD_res_darkcausality[[3]] %>% replace(is.na(.), 0)
ASTPP_ASD_res_darkcausality[[4]] <- ASTPP_ASD_res_darkcausality[[4]] %>% replace(is.na(.), 0)
ASTPP_ASD_res_darkcausality_sig <- sigPC(ASTPP_ASD_res_darkcausality[[2]], ASTPP_ASD_res_darkcausality[[3]], ASTPP_ASD_res_darkcausality[[4]])
ASTPP_Control_res_darkcausality[[2]] <- ASTPP_Control_res_darkcausality[[2]] %>% replace(is.na(.), 0)
ASTPP_Control_res_darkcausality[[3]] <- ASTPP_Control_res_darkcausality[[3]] %>% replace(is.na(.), 0)
ASTPP_Control_res_darkcausality[[4]] <- ASTPP_Control_res_darkcausality[[4]] %>% replace(is.na(.), 0)
ASTPP_Control_res_darkcausality_sig <- sigPC(ASTPP_Control_res_darkcausality[[2]], ASTPP_Control_res_darkcausality[[3]], ASTPP_Control_res_darkcausality[[4]])
ASTPP_ASD_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(ASTPP_ASD_res_darkcausality_sig[[1]] + ASTPP_ASD_res_darkcausality_sig[[2]] + ASTPP_ASD_res_darkcausality_sig[[3]]))
ASTPP_Control_res_darkcausality_graph <- graph_from_biadjacency_matrix(t(ASTPP_Control_res_darkcausality_sig[[1]] + ASTPP_Control_res_darkcausality_sig[[2]] + ASTPP_Control_res_darkcausality_sig[[3]]))

############################################################################ Incorporating priori information of lncRNA targets #########################################################################
lncRTarget_priori <- as.matrix(read.csv("LncTar.csv", header = TRUE, sep=","))
lncRTarget_priori_graph <- make_graph(c(t(lncRTarget_priori[, 1:2])), directed = FALSE)

ASD_res_darkcausality_priori_graph <- ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
Control_res_darkcausality_priori_graph <- Control_res_darkcausality_graph %s% lncRTarget_priori_graph

ACC_ASD_res_darkcausality_priori_graph <- ACC_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
ACC_Control_res_darkcausality_priori_graph <- ACC_Control_res_darkcausality_graph %s% lncRTarget_priori_graph
PFC_ASD_res_darkcausality_priori_graph <- PFC_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
PFC_Control_res_darkcausality_priori_graph <- PFC_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

Lower18_ASD_res_darkcausality_priori_graph <- Lower18_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
Lower18_Control_res_darkcausality_priori_graph <- Lower18_Control_res_darkcausality_graph %s% lncRTarget_priori_graph
Larger18_ASD_res_darkcausality_priori_graph <- Larger18_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
Larger18_Control_res_darkcausality_priori_graph <- Larger18_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

Male_ASD_res_darkcausality_priori_graph <- Male_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
Male_Control_res_darkcausality_priori_graph <- Male_Control_res_darkcausality_graph %s% lncRTarget_priori_graph
Female_ASD_res_darkcausality_priori_graph <- Female_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
Female_Control_res_darkcausality_priori_graph <- Female_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

NeuNRGNII_ASD_res_darkcausality_priori_graph <- NeuNRGNII_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
NeuNRGNII_Control_res_darkcausality_priori_graph <- NeuNRGNII_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

L56_ASD_res_darkcausality_priori_graph <- L56_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
L56_Control_res_darkcausality_priori_graph <- L56_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

Oligodendrocytes_ASD_res_darkcausality_priori_graph <- Oligodendrocytes_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
Oligodendrocytes_Control_res_darkcausality_priori_graph <- Oligodendrocytes_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

OPC_ASD_res_darkcausality_priori_graph <- OPC_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
OPC_Control_res_darkcausality_priori_graph <- OPC_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

ASTFB_ASD_res_darkcausality_priori_graph <- ASTFB_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
ASTFB_Control_res_darkcausality_priori_graph <- ASTFB_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

Endothelial_ASD_res_darkcausality_priori_graph <- Endothelial_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
Endothelial_Control_res_darkcausality_priori_graph <- Endothelial_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

Microglia_ASD_res_darkcausality_priori_graph <- Microglia_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
Microglia_Control_res_darkcausality_priori_graph <- Microglia_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

NeuNRGNI_ASD_res_darkcausality_priori_graph <- NeuNRGNI_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
NeuNRGNI_Control_res_darkcausality_priori_graph <- NeuNRGNI_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

INVIP_ASD_res_darkcausality_priori_graph <- INVIP_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
INVIP_Control_res_darkcausality_priori_graph <- INVIP_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

L56CC_ASD_res_darkcausality_priori_graph <- L56CC_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
L56CC_Control_res_darkcausality_priori_graph <- L56CC_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

INSV2C_ASD_res_darkcausality_priori_graph <- INSV2C_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
INSV2C_Control_res_darkcausality_priori_graph <- INSV2C_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

L23_ASD_res_darkcausality_priori_graph <- L23_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
L23_Control_res_darkcausality_priori_graph <- L23_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

INPV_ASD_res_darkcausality_priori_graph <- INPV_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
INPV_Control_res_darkcausality_priori_graph <- INPV_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

L4_ASD_res_darkcausality_priori_graph <- L4_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
L4_Control_res_darkcausality_priori_graph <- L4_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

INSST_ASD_res_darkcausality_priori_graph <- INSST_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
INSST_Control_res_darkcausality_priori_graph <- INSST_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

Neumat_ASD_res_darkcausality_priori_graph <- Neumat_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
Neumat_Control_res_darkcausality_priori_graph <- Neumat_Control_res_darkcausality_graph %s% lncRTarget_priori_graph

ASTPP_ASD_res_darkcausality_priori_graph <- ASTPP_ASD_res_darkcausality_graph %s% lncRTarget_priori_graph
ASTPP_Control_res_darkcausality_priori_graph <- ASTPP_Control_res_darkcausality_graph %s% lncRTarget_priori_graph
```

## Step 4: Validation with and without priori information
```{r, eval=TRUE, include=TRUE}
############################# 4.1 Validation with priori information #############################
lncRTarget_groundtruth <- as.matrix(read.csv("RegNetwork_high+medium.csv", header = TRUE, sep=","))
lncRTarget_groundtruth_graph <- make_graph(c(t(lncRTarget_groundtruth[, 1:2])), directed = FALSE)

ASD_res_darkcausality_priori_validated <- as_data_frame(ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
Control_res_darkcausality_priori_validated <- as_data_frame(Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

ACC_ASD_res_darkcausality_priori_validated <- as_data_frame(ACC_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
ACC_Control_res_darkcausality_priori_validated <- as_data_frame(ACC_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
PFC_ASD_res_darkcausality_priori_validated <- as_data_frame(PFC_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
PFC_Control_res_darkcausality_priori_validated <- as_data_frame(PFC_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

Lower18_ASD_res_darkcausality_priori_validated <- as_data_frame(Lower18_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
Lower18_Control_res_darkcausality_priori_validated <- as_data_frame(Lower18_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
Larger18_ASD_res_darkcausality_priori_validated <- as_data_frame(Larger18_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
Larger18_Control_res_darkcausality_priori_validated <- as_data_frame(Larger18_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

Male_ASD_res_darkcausality_priori_validated <- as_data_frame(Male_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
Male_Control_res_darkcausality_priori_validated <- as_data_frame(Male_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
Female_ASD_res_darkcausality_priori_validated <- as_data_frame(Female_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
Female_Control_res_darkcausality_priori_validated <- as_data_frame(Female_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

NeuNRGNII_ASD_res_darkcausality_priori_validated <- as_data_frame(NeuNRGNII_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
NeuNRGNII_Control_res_darkcausality_priori_validated <- as_data_frame(NeuNRGNII_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

L56_ASD_res_darkcausality_priori_validated <- as_data_frame(L56_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
L56_Control_res_darkcausality_priori_validated <- as_data_frame(L56_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

Oligodendrocytes_ASD_res_darkcausality_priori_validated <- as_data_frame(Oligodendrocytes_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
Oligodendrocytes_Control_res_darkcausality_priori_validated <- as_data_frame(Oligodendrocytes_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

OPC_ASD_res_darkcausality_priori_validated <- as_data_frame(OPC_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
OPC_Control_res_darkcausality_priori_validated <- as_data_frame(OPC_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

ASTFB_ASD_res_darkcausality_priori_validated <- as_data_frame(ASTFB_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
ASTFB_Control_res_darkcausality_priori_validated <- as_data_frame(ASTFB_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

Endothelial_ASD_res_darkcausality_priori_validated <- as_data_frame(Endothelial_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
Endothelial_Control_res_darkcausality_priori_validated <- as_data_frame(Endothelial_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

Microglia_ASD_res_darkcausality_priori_validated <- as_data_frame(Microglia_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
Microglia_Control_res_darkcausality_priori_validated <- as_data_frame(Microglia_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

NeuNRGNI_ASD_res_darkcausality_priori_validated <- as_data_frame(NeuNRGNI_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
NeuNRGNI_Control_res_darkcausality_priori_validated <- as_data_frame(NeuNRGNI_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

INVIP_ASD_res_darkcausality_priori_validated <- as_data_frame(INVIP_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
INVIP_Control_res_darkcausality_priori_validated <- as_data_frame(INVIP_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

L56CC_ASD_res_darkcausality_priori_validated <- as_data_frame(L56CC_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
L56CC_Control_res_darkcausality_priori_validated <- as_data_frame(L56CC_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

INSV2C_ASD_res_darkcausality_priori_validated <- as_data_frame(INSV2C_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
INSV2C_Control_res_darkcausality_priori_validated <- as_data_frame(INSV2C_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

L23_ASD_res_darkcausality_priori_validated <- as_data_frame(L23_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
L23_Control_res_darkcausality_priori_validated <- as_data_frame(L23_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

INPV_ASD_res_darkcausality_priori_validated <- as_data_frame(INPV_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
INPV_Control_res_darkcausality_priori_validated <- as_data_frame(INPV_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

L4_ASD_res_darkcausality_priori_validated <- as_data_frame(L4_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
L4_Control_res_darkcausality_priori_validated <- as_data_frame(L4_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

INSST_ASD_res_darkcausality_priori_validated <- as_data_frame(INSST_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
INSST_Control_res_darkcausality_priori_validated <- as_data_frame(INSST_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

Neumat_ASD_res_darkcausality_priori_validated <- as_data_frame(Neumat_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
Neumat_Control_res_darkcausality_priori_validated <- as_data_frame(Neumat_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

ASTPP_ASD_res_darkcausality_priori_validated <- as_data_frame(ASTPP_ASD_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)
ASTPP_Control_res_darkcausality_priori_validated <- as_data_frame(ASTPP_Control_res_darkcausality_priori_graph %s% lncRTarget_groundtruth_graph)

############################# 4.2 Validation without priori information #############################
ASD_res_darkcausality_validated <- as_data_frame(ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
Control_res_darkcausality_validated <- as_data_frame(Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

ACC_ASD_res_darkcausality_validated <- as_data_frame(ACC_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
ACC_Control_res_darkcausality_validated <- as_data_frame(ACC_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
PFC_ASD_res_darkcausality_validated <- as_data_frame(PFC_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
PFC_Control_res_darkcausality_validated <- as_data_frame(PFC_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

Lower18_ASD_res_darkcausality_validated <- as_data_frame(Lower18_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
Lower18_Control_res_darkcausality_validated <- as_data_frame(Lower18_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
Larger18_ASD_res_darkcausality_validated <- as_data_frame(Larger18_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
Larger18_Control_res_darkcausality_validated <- as_data_frame(Larger18_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

Male_ASD_res_darkcausality_validated <- as_data_frame(Male_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
Male_Control_res_darkcausality_validated <- as_data_frame(Male_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
Female_ASD_res_darkcausality_validated <- as_data_frame(Female_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
Female_Control_res_darkcausality_validated <- as_data_frame(Female_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

NeuNRGNII_ASD_res_darkcausality_validated <- as_data_frame(NeuNRGNII_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
NeuNRGNII_Control_res_darkcausality_validated <- as_data_frame(NeuNRGNII_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

L56_ASD_res_darkcausality_validated <- as_data_frame(L56_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
L56_Control_res_darkcausality_validated <- as_data_frame(L56_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

Oligodendrocytes_ASD_res_darkcausality_validated <- as_data_frame(Oligodendrocytes_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
Oligodendrocytes_Control_res_darkcausality_validated <- as_data_frame(Oligodendrocytes_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

OPC_ASD_res_darkcausality_validated <- as_data_frame(OPC_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
OPC_Control_res_darkcausality_validated <- as_data_frame(OPC_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

ASTFB_ASD_res_darkcausality_validated <- as_data_frame(ASTFB_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
ASTFB_Control_res_darkcausality_validated <- as_data_frame(ASTFB_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

Endothelial_ASD_res_darkcausality_validated <- as_data_frame(Endothelial_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
Endothelial_Control_res_darkcausality_validated <- as_data_frame(Endothelial_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

Microglia_ASD_res_darkcausality_validated <- as_data_frame(Microglia_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
Microglia_Control_res_darkcausality_validated <- as_data_frame(Microglia_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

NeuNRGNI_ASD_res_darkcausality_validated <- as_data_frame(NeuNRGNI_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
NeuNRGNI_Control_res_darkcausality_validated <- as_data_frame(NeuNRGNI_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

INVIP_ASD_res_darkcausality_validated <- as_data_frame(INVIP_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
INVIP_Control_res_darkcausality_validated <- as_data_frame(INVIP_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

L56CC_ASD_res_darkcausality_validated <- as_data_frame(L56CC_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
L56CC_Control_res_darkcausality_validated <- as_data_frame(L56CC_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

INSV2C_ASD_res_darkcausality_validated <- as_data_frame(INSV2C_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
INSV2C_Control_res_darkcausality_validated <- as_data_frame(INSV2C_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

L23_ASD_res_darkcausality_validated <- as_data_frame(L23_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
L23_Control_res_darkcausality_validated <- as_data_frame(L23_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

INPV_ASD_res_darkcausality_validated <- as_data_frame(INPV_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
INPV_Control_res_darkcausality_validated <- as_data_frame(INPV_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

L4_ASD_res_darkcausality_validated <- as_data_frame(L4_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
L4_Control_res_darkcausality_validated <- as_data_frame(L4_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

INSST_ASD_res_darkcausality_validated <- as_data_frame(INSST_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
INSST_Control_res_darkcausality_validated <- as_data_frame(INSST_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

Neumat_ASD_res_darkcausality_validated <- as_data_frame(Neumat_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
Neumat_Control_res_darkcausality_validated <- as_data_frame(Neumat_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)

ASTPP_ASD_res_darkcausality_validated <- as_data_frame(ASTPP_ASD_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
ASTPP_Control_res_darkcausality_validated <- as_data_frame(ASTPP_Control_res_darkcausality_graph %s% lncRTarget_groundtruth_graph)
```

## Step 5: Heterogeneity analysis
```{r, eval=TRUE, include=TRUE}
lncR_diagnostic_net <- list(ASD_res_darkcausality_priori_graph, Control_res_darkcausality_priori_graph)
lncR_region_net <- list(ACC_ASD_res_darkcausality_priori_graph,
                        PFC_ASD_res_darkcausality_priori_graph,
                        ACC_Control_res_darkcausality_priori_graph,                        
                        PFC_Control_res_darkcausality_priori_graph)
lncR_age_net <- list(Lower18_ASD_res_darkcausality_priori_graph,
                     Larger18_ASD_res_darkcausality_priori_graph,
                     Lower18_Control_res_darkcausality_priori_graph,
		     Larger18_Control_res_darkcausality_priori_graph)
lncR_sex_net <- list(Male_ASD_res_darkcausality_priori_graph,
                     Female_ASD_res_darkcausality_priori_graph,
		     Male_Control_res_darkcausality_priori_graph,
		     Female_Control_res_darkcausality_priori_graph)
lncR_celltype_net <- list(NeuNRGNII_ASD_res_darkcausality_priori_graph,
                     L56_ASD_res_darkcausality_priori_graph,
                     Oligodendrocytes_ASD_res_darkcausality_priori_graph,
		     OPC_ASD_res_darkcausality_priori_graph,
                     ASTFB_ASD_res_darkcausality_priori_graph,
                     Endothelial_ASD_res_darkcausality_priori_graph,
                     Microglia_ASD_res_darkcausality_priori_graph,
		     NeuNRGNI_ASD_res_darkcausality_priori_graph,
		     INVIP_ASD_res_darkcausality_priori_graph,
		     L56CC_ASD_res_darkcausality_priori_graph,
		     INSV2C_ASD_res_darkcausality_priori_graph,
		     L23_ASD_res_darkcausality_priori_graph,
		     INPV_ASD_res_darkcausality_priori_graph,
		     L4_ASD_res_darkcausality_priori_graph,
		     INSST_ASD_res_darkcausality_priori_graph,
		     Neumat_ASD_res_darkcausality_priori_graph,
		     ASTPP_ASD_res_darkcausality_priori_graph,
                     NeuNRGNII_Control_res_darkcausality_priori_graph,
                     L56_Control_res_darkcausality_priori_graph,
                     Oligodendrocytes_Control_res_darkcausality_priori_graph,
		     OPC_Control_res_darkcausality_priori_graph,
                     ASTFB_Control_res_darkcausality_priori_graph,
                     Endothelial_Control_res_darkcausality_priori_graph,
                     Microglia_Control_res_darkcausality_priori_graph,
		     NeuNRGNI_Control_res_darkcausality_priori_graph,
		     INVIP_Control_res_darkcausality_priori_graph,
		     L56CC_Control_res_darkcausality_priori_graph,
		     INSV2C_Control_res_darkcausality_priori_graph,
		     L23_Control_res_darkcausality_priori_graph,
		     INPV_Control_res_darkcausality_priori_graph,
		     L4_Control_res_darkcausality_priori_graph,
		     INSST_Control_res_darkcausality_priori_graph,
		     Neumat_Control_res_darkcausality_priori_graph,
		     ASTPP_Control_res_darkcausality_priori_graph
                     )
diagnostic_Het <- Het.network(lncR_diagnostic_net, lncR_diagnostic_net)
region_Het <- Het.network(lncR_region_net, lncR_region_net)
age_Het <- Het.network(lncR_age_net, lncR_age_net)
sex_Het <- Het.network(lncR_sex_net, lncR_sex_net)
celltype_Het <- Het.network(lncR_celltype_net, lncR_celltype_net)
```

# Conclusions
In this tutorial, we apply Clean, Granger and seqICP to show how to infer dynamic lncRNA causal regulation in ASD. Moreover, we also perform heterogeneity analysis of the identified lncRNA causal regulatory networks across diverse brain biological contexts (i.e. diagnosis, region, age, sex and cell type). Taken together, Clean provides a useful method to help delineate dynamic lncRNA causal regulation in ASD, and offers technical support for precision therapeutics tailored to dynamic causal regulation states.

# Session information
```{r}
sessionInfo()
```
